DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/intro.tex
Adjust paper roadmap in intro
The previous roadmap covered the incorrect sections.

The remaining sections of the paper are as follows: Section II gives
an overview of the platform, including the high-level system and the
methods used for training and inference. Section III discusses the
ways/methodologies in which training data was collected. Section IV
outlines the network architecture. This is followed by the real-time
DNN inferencing in Section V. Section VI reviews the online/offline
training done with the platform, with an evaluation given in Section
VII. Section VIII gives a discussion of related works, and the paper
finishes with conclusions in Section IX.

>>>>

The remaining sections of the paper are as follows: Section II 
provides a background of applications in autonomous driving. Section 
III gives an overview of the DeepPicar platform, including the 
high-level system and the methods used for training and inference. 
Section IV presents our evaluation of the platform and how different 
factors can affect performance. Section V gives a comparison between 
the Raspberry Pi 3 and other embedded computing platforms to 
determine their suitably for autonomous driving research. Related 
works are discussed in Section VI, and the paper finishes with 
conclusions in Section VII.
